### 2020-04-28 final_report/appendix_online.tex
fill online appendix

TODO: point reader to various online repositories, briefly describe them

\begin{enumerate}
	\item data repository
	\item sampling repository
	\item regression repository
	\item hyperopt repository
	\item docs repository
\end{enumerate}

>>>>

In this appendix, we provide a brief overview of datasets, open-source
software, documentation resources and other materials available online for
public use. All files related to this project are hosted by GitHub in
a group at \url{https://github.com/ucl-tbr-group-project}, organised in the
following repositories:
\begin{description}
	\item[\href{https://github.com/ucl-tbr-group-project/simple-sphere-study}{Simple Sphere Study}]
		OpenMC TBR simulation software used to generate TBR values.
	\item[\href{https://github.com/ucl-tbr-group-project/sampling}{Sampling}]
		Python implementation of the Approximate TBR Evaluator.
	\item[\href{https://github.com/ucl-tbr-group-project/data}{Data}]
		Over \num{900000}~datapoints and TBR values generated in sampling runs 0-2.
	\item[\href{https://github.com/ucl-tbr-group-project/regression}{Regression}]
		Python implementation of the surrogate models presented in this work as
		well as various pre-processing, plotting and evaluation tools.
	\item[\href{https://github.com/ucl-tbr-group-project/hyperopt}{Hyperparameter Optimisation}]
		Results of experiments 1-4, including performance plots and software
		commands used to produce them.
	\item[\href{https://github.com/ucl-tbr-group-project/documentation}{Documentation}]
		Project notes, extended bibliography, a digital version of this
		\LaTeX\  document and source files for all presented figures and
		tables.
\end{description}

Unless specified otherwise, permission to use these materials is hereby granted
in accordance with the MIT~Licence.
